---
title: "Data For A Deep Classification Model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparing_Optimizers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

Overall, the process for classification is very similar to the regression process. The main difference is to select the final activation to force a probability to be created.

## Matrices and Activations

First a list of matrices must be made. The elements of each matrix are the Betas of the network. The dimensions are associated with the network's structure. Here is an example of creating ideal data for a network with 3 hidden layers. The first hidden layer has 10 nodes. The second hidden layer has 8 nodes. The third hidden layer has 5 nodes.

```{r  deep1}
library(NeuralNetworkSimulatoR)

set.seed(1)
M <- list(
  matrix(rnorm(12*10, mean = 0, sd = 1), nrow = 12, ncol = 10),
  matrix(rnorm(10*8, mean = 0, sd = 1), nrow = 10, ncol = 8),
  matrix(rnorm(8*5, mean = 0, sd = 1), nrow = 8, ncol = 5),
  matrix(rnorm(5*1, mean = 0, sd = 1), nrow = 5, ncol = 1)
  )
```

Next activation functions for each hidden layer are selected. In this example, the first three activations are relu and the last is sigmoid.
```{r  deep2}
A <- list(relu_R, 
          relu_R,
          relu_R,
          sigmoid_R)
```

## Creating Data
With the matrices and activations created, a data set containing 12 input variables following a normal distribution is made.

```{r  deep3}
simData <- simulate_classification_data(
  rows = 1000L,
  N = 12L, U = 0L, C = 0L,
  matrices = M, activations = A
)

head(simData)
```

A data set with only categorical variables can also be created.
```{r  deep4}
simData <- simulate_classification_data(
  rows = 1000L,
  N = 0L, U = 0L, C = 12L,
  matrices = M, activations = A
)

head(simData)
```

Or a mixture of normal, uniform and categorical variables.
```{r  deep5}
simData <- simulate_classification_data(
  rows = 1000L,
  N = 6L, U = 3L, C = 3L,
  matrices = M, activations = A
)

head(simData)
```
